Deciding Bitvector Termination with Program Synthesis

### 2014-07-02 papers/termination/paper.tex
sec 6
Nudges

Gupta et al. \cite{DBLP:conf/popl/GuptaHMRX08} characterize non-termination of a transition relation $T$ by the existence of an \emph{(open) recurrence set},
i.e. a nonempty set of states $N$ such that for each $s \in N$ there
exists a transition to some $s'\in N$. 
For our case, given a loop $L = (I,x,G,T)$, the notion of open recurrent set is encoded by Definition~\ref{def:nonterm-formula}.

@@

In order to formulate the non-termination problem inside the synthesis fragment, 
we make use of the notion of \emph{closed recurrence set} introduced by Chen et al. in \cite{DBLP:conf/tacas/ChenCFNO14}. 
As opposed to a closed recurrence set, this is a  purely universal property: for each state in the recurrence set $N$, each of its successors 
must be in $N$. Thus, the non-termination problem becomes equivalent to the
satisfiability of Definition~\ref{def:deterministic-nonterm-formula}.
As our formulation is with respect to a given loop $L=(x,I,G,t)$, we require the  
recurrence set to include the loop's guard, $N(x) \rightarrow G(x)$. In other words, the loop's guard needs to be satisfied in order for the 
infinite execution to happen.

>>>>

Gupta et al. \cite{DBLP:conf/popl/GuptaHMRX08} characterize non-termination of a transition relation $T$ by the existence of an \emph{(open) recurrence set},
i.e. a nonempty set of states $N$ such that for each $s \in N$ there
exists a transition to some $s'\in N$. 
For our case, given a loop $L = \langle I,G,T \rangle$, the notion of open recurrent set is encoded by Definition~\ref{def:nonterm-formula}.

@@

In order to formulate the non-termination problem inside the synthesis fragment, 
we make use of the notion of \emph{closed recurrence set} introduced by Chen et al. in \cite{DBLP:conf/tacas/ChenCFNO14}. 
As opposed to a closed recurrence set, this is a  purely universal property: for each state in the recurrence set $N$, each of its successors 
must be in $N$. Thus, the non-termination problem becomes equivalent to the
satisfiability of Definition~\ref{def:deterministic-nonterm-formula}.
As our formulation is with respect to a given loop $L=\langle I,G,t \rangle$, we require the  
recurrence set to include the loop's guard, $N(x) \rightarrow G(x)$. In other words, the loop's guard needs to be satisfied in order for the 
infinite execution to happen.
